Contextual Combinatorial Cascading Bandits

### 2015-12-04 contextual combinatorial cascading bandits.tex

The above formulation is on disjuctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result. Similarly, we could also consider the case of conjunctive objective. We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$. The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
$$
At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward
	$\br_{\wedge, t}$:
\begin{align*}
\br_{\wedge, t} &= \begin{cases}
\gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
\end{cases}\\
&=\begin{cases}
\gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
\end{cases}
\end{align*}

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent
	chooses her action. 
By Equation \eqref{eq:expectation}, we have 
$$
\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
\{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. 
%In the following, we will mainly use notations for disjunctive objective when the two cases are similar.

@@

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. Second, it recommends an action $\bA_t$ by the offline oracle with estimated weights $\bU_t$. Third, play $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 1, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent update $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stack A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1' x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t}' x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1' \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t}' \bw_t(\ba_{\bO_t}^t)]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}

>>>>

The above formulation is on the disjunctive objective, that is, at a time step the agent stops as soon as she reveals a base arm at a position $k$ in the sequence with weight $1$ and she receives reward $\gamma_k$ as the result. Similarly, we could also consider the case of conjunctive objective. We also use Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ to indicate the weight of item $a$ at time $t$ satisfying Equation \eqref{eq:expectation}). The learning agent observes all items until the first one with weight $0$. Suppose we also consider partial reward: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $\gamma_k'$; if all items have weight $1$, the learning agent receives reward $1$. The more items the learning agent reveals, the more reward the agent should receive. It is reasonable to assume that
$$
0 = \gamma'_1 \leq \gamma'_2 \leq \cdots \leq \gamma'_K \leq 1.
$$
At the end of time $t$, the learning agent observes $\bO_{\wedge, t}, \bw_t(\ba_k^t), k \leq \bO_{\wedge, t}$ and receives reward
	$\br_{\wedge, t}$:
\begin{align*}
\br_{\wedge, t} &= \begin{cases}
\gamma_{\bO_{\wedge, t}}'  &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{\bO_{\wedge, t}}^t) = 1,
\end{cases}\\
&=\begin{cases}
\gamma_{k}'  &\text{if } \bw_t(\ba_{i}^t) = 1, i < k, \bw_t(\ba_{k}^t) = 0,\\
1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t}.
\end{cases}
\end{align*}

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent
	chooses her action. 
By Equation \eqref{eq:expectation}, we have 
$$
\EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
\{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix. 
In the following, we will mainly use notations for the disjunctive objective when the two cases are similar.

@@

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. 
First, the learning agent 
	computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all base arms in $E$. 
Second, she uses the computed UCBs $\bU_t$ to select an action $\bA_t$. 
Third, she plays $\bA_t$ and observes all feedback of base arms until first $0$ weight come out; the learning agent observes $\bO_t$ base arms and $\bw_t(\ba_k^t), k \in [\bO_t]$, where 
$$
\bw_t(\ba_{k}^t) = \begin{cases} 0, ~~k < \bO_t\\ 1, ~~k = \bO_t\end{cases}
$$ 
or
$$
\bw_t(\ba_k^t) = 0, k \leq \bO_t = \abs{\bA_t}.
$$
Then, the learning agent updates $\bV_t, \bX_t, \bY_t$ in order to get a newer estimate $\hat{\theta}_t$ of $\theta_*$ and new confidence radius $\beta_t(\delta)$. In this part, we use the notation $[A; B]$ to denote the matrix obtained by stacking A and B vertically like
 $\begin{pmatrix} A\\ B\end{pmatrix}$.

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}
